Cryptanalysis of \MORUS

### 2018-05-17 morusAC_00_Abstract.tex
removed extra word in abstract
typo

  As our main result, we present a
  linear correlation in the keystream of full \MORUS, which can be used to distinguish its output
  from random and to recover some plaintext bits in the
  broadcast setting.  For \MORUS[1280], the correlation is $2^{-76}$,
  which can be exploited after around $2^{152}$ encryptions, less than
  would be expected for a 256-bit secure cipher.  For
  \MORUS[640], the same attack results in a correlation of $2^{-73}$, which does not threaten
  violate the security claims of the cipher.

@@

\keywords{MORUS, CAESAR, Authenticated Encryption, Nonce Respect, Linear Cryptanalysis, Confidentiality.}
\end{abstract}

>>>>

  As our main result, we present a
  linear correlation in the keystream of full \MORUS, which can be used to distinguish its output
  from random and to recover some plaintext bits in the
  broadcast setting.  For \MORUS[1280], the correlation is $2^{-76}$,
  which can be exploited after around $2^{152}$ encryptions, less than
  would be expected for a 256-bit secure cipher.  For
  \MORUS[640], the same attack results in a correlation of $2^{-73}$, which does not
  violate the security claims of the cipher.

@@

\keywords{MORUS, CAESAR, Authenticated Encryption, Nonce Respecting, Linear Cryptanalysis, Confidentiality.}
\end{abstract}
